---
title: "Automation Runs Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme:
      version: 4
      bootswatch: slate
    self_contained: true
css: styles.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(plotly)
library(googlesheets4)
library(scales)
library(htmltools)
library(zoo)  # For rolling averages
library(reactable)  # For interactive tables

# flexdashboard: passing caption= replaces the whole caption and drops the ### title — keep both via HTML
vb_caption <- function(title, detail) {
  HTML(sprintf(
    '<span class="vb-title">%s</span><span class="vb-detail">%s</span>',
    htmlEscape(title),
    htmlEscape(detail, attribute = FALSE)
  ))
}

# ============================
# CONFIG
# ============================
# Auth: GOOGLE_SA_JSON (full JSON string) for Posit Connect; GOOGLE_SA_JSON_PATH for local dev
GOOGLE_SA_JSON <- Sys.getenv("GOOGLE_SA_JSON", unset = "")
GOOGLE_SA_JSON_PATH <- Sys.getenv("GOOGLE_SA_JSON_PATH", unset = "")
AUTOMATION_SHEET_ID <- Sys.getenv("AUTOMATION_SHEET_ID", unset = "")
AUTOMATION_SHEET_TAB <- Sys.getenv("AUTOMATION_SHEET_TAB", unset = "UI")
RELEASE_DEPLOYMENT_SHEET_TAB <- Sys.getenv("RELEASE_DEPLOYMENT_SHEET_TAB", unset = "Release Deployment")
RUNS_SHEET_RANGE <- Sys.getenv("RUNS_SHEET_RANGE", unset = "A:D")
RUNS_TZ <- Sys.getenv("RUNS_TZ", unset = "UTC")

# ============================
# DESIGN SYSTEM (MATCH SHORTCUT)
# ============================
BASE_THEME <- theme_minimal(base_size = 12) +
  theme(
    plot.background = element_rect(fill = "#1f1f1f", color = NA),
    panel.background = element_rect(fill = "#1f1f1f", color = NA),
    panel.grid.major = element_line(color = "#333333"),
    panel.grid.minor = element_blank(),
    text = element_text(color = "#e6e6e6"),
    axis.text = element_text(color = "#cccccc"),
    axis.title = element_text(color = "#cccccc"),
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(color = "#aaaaaa"),
    legend.background = element_rect(fill = "#1f1f1f"),
    legend.key = element_rect(fill = "#1f1f1f"),
    legend.text = element_text(color = "#e6e6e6"),
    legend.title = element_text(color = "#e6e6e6")
  )

plotly_title <- function(text) {
  list(
    text = paste0("<b>", text, "</b>"),
    x = 0.02,
    xanchor = "left",
    font = list(size = 14, color = "#e6e6e6")
  )
}

add_plotly_border <- function(p, color = "#333333", width = 1) {
  p %>% layout(
    shapes = list(
      list(
        type = "rect",
        xref = "paper", yref = "paper",
        x0 = 0, y0 = 0, x1 = 1, y1 = 1,
        line = list(color = color, width = width),
        fillcolor = "rgba(0,0,0,0)"
      )
    )
  )
}

# Goal reference: Paul Tol wine — CB-safe, distinct from pass-rate cyan (#5bc0de)
GOAL_LINE_COLOR <- "#882255"
AUTOMATION_PASS_RATE_GOAL <- 0.85
RELEASE_PASS_RATE_GOAL <- 0.95

# ============================
# TREND ANALYSIS HELPERS
# ============================
# flexdashboard caption helper for title + detail
vb_caption <- function(title, detail) {
  HTML(sprintf(
    '<span class="vb-title">%s</span><span class="vb-detail">%s</span>',
    htmlEscape(title),
    htmlEscape(detail, attribute = FALSE)
  ))
}

# Reactable theme for dark mode
REACTABLE_THEME_DARK <- reactableTheme(
  color = "#e6e6e6",
  backgroundColor = "#1f1f1f",
  borderColor = "#333333",
  stripedColor = "#242424",
  highlightColor = "#2b2b2b",
  cellPadding = "10px 12px",
  style = list(fontSize = "13px"),
  headerStyle = list(
    backgroundColor = "#1a1a1a",
    color = "#e6e6e6",
    borderColor = "#333333",
    fontWeight = 600
  ),
  tableBodyStyle = list(borderColor = "#333333")
)

# Rolling average calculation
calc_rolling_avg <- function(df, date_col, value_col, window_days = 7) {
  df %>%
    mutate({{ date_col }} := as.Date({{ date_col }})) %>%
    arrange({{ date_col }}) %>%
    mutate(
      rolling_avg = roll_mean({{ value_col }},
        n = window_days,
        align = "right",
        fill = NA
      )
    )
}

# Linear regression trend line
calc_trend_line <- function(df, date_col, value_col) {
  df <- df %>% mutate({{ date_col }} := as.Date({{ date_col }}))
  df <- df %>% mutate(day_num = as.numeric({{ date_col }} - min({{ date_col }}, na.rm = TRUE)))
  
  valid <- df %>% filter(!is.na({{ value_col }}) & !is.na(day_num))
  if (nrow(valid) < 2) return(df %>% mutate(trend = NA_real_))
  
  model <- lm(as.formula(paste0("`", value_col, "` ~ day_num")), data = valid)
  df <- df %>% mutate(trend = predict(model, newdata = df))
  
  df %>% select(-day_num)
}

# ============================
# ANOMALY DETECTION HELPERS
# ============================
# Detect statistical outliers using IQR method
detect_anomalies_iqr <- function(df, value_col, multiplier = 1.5) {
  values <- df %>% pull({{ value_col }}) %>% na.omit()
  if (length(values) < 4) return(rep(FALSE, nrow(df)))
  
  q1 <- quantile(values, 0.25)
  q3 <- quantile(values, 0.75)
  iqr <- q3 - q1
  lower <- q1 - multiplier * iqr
  upper <- q3 + multiplier * iqr
  
  df %>% mutate(
    is_anomaly = {{ value_col }} < lower | {{ value_col }} > upper,
    anomaly_type = case_when(
      {{ value_col }} < lower ~ "low",
      {{ value_col }} > upper ~ "high",
      TRUE ~ NA_character_
    )
  )
}

# Z-score based anomaly detection
detect_anomalies_zscore <- function(df, value_col, threshold = 2) {
  values <- df %>% pull({{ value_col }}) %>% na.omit()
  if (length(values) < 4) return(df %>% mutate(is_anomaly = FALSE, z_score = NA_real_))
  
  mean_val <- mean(values)
  sd_val <- sd(values)
  if (sd_val == 0) return(df %>% mutate(is_anomaly = FALSE, z_score = 0))
  
  df %>% mutate(
    z_score = abs(({{ value_col }} - mean_val) / sd_val),
    is_anomaly = z_score > threshold
  )
}

# Trend direction indicator
get_trend_direction <- function(df, value_col) {
  if (nrow(df) < 2) return("stable")
  
  recent <- df %>% filter(!is.na({{ value_col }})) %>% tail(7)
  if (nrow(recent) < 2) return("stable")
  
  first_val <- recent %>% head(1) %>% pull({{ value_col }})
  last_val <- recent %>% tail(1) %>% pull({{ value_col }})
  
  diff_pct <- (last_val - first_val) / first_val
  
  if (diff_pct > 0.02) return("improving")
  if (diff_pct < -0.02) return("declining")
  "stable"
}

pass_rate_goal_gg_hline <- function(yintercept) {
  geom_hline(
    yintercept = yintercept,
    color = GOAL_LINE_COLOR,
    linetype = "dashed",
    linewidth = 0.7,
    inherit.aes = FALSE
  )
}

pass_rate_goal_annotation <- function(goal) {
  list(
    list(
      xref = "paper",
      x = 0.02,
      yref = "y",
      y = goal,
      text = paste0("Goal (", scales::percent(goal, accuracy = 1), ")"),
      showarrow = FALSE,
      xanchor = "left",
      font = list(color = GOAL_LINE_COLOR, size = 11),
      bgcolor = "rgba(31,31,31,0.88)",
      bordercolor = GOAL_LINE_COLOR,
      borderwidth = 1,
      borderpad = 4
    )
  )
}

# ============================
# DATA
# ============================
auth_gs <- function() {
  if (nzchar(GOOGLE_SA_JSON)) {
    googlesheets4::gs4_auth(path = GOOGLE_SA_JSON)  # path accepts JSON string (Posit Connect)
  } else if (nzchar(GOOGLE_SA_JSON_PATH) && file.exists(GOOGLE_SA_JSON_PATH)) {
    googlesheets4::gs4_auth(path = GOOGLE_SA_JSON_PATH)
  } else {
    stop("Set GOOGLE_SA_JSON (Posit Connect) or GOOGLE_SA_JSON_PATH (local) with valid credentials")
  }
}

read_runs <- function() {
  auth_gs()
  googlesheets4::read_sheet(
    ss = AUTOMATION_SHEET_ID,
    sheet = AUTOMATION_SHEET_TAB,
    range = RUNS_SHEET_RANGE,
    col_types = "cccc"
  )
}

clean_runs <- function(df) {
  df %>%
    rename_with(~str_trim(.x)) %>%
    mutate(
      Date = parse_date_time(
        Date,
        orders = c("ymd HMS", "mdy HMS", "ymd HM", "mdy HM", "ymd", "mdy"),
        tz = RUNS_TZ
      ),
      `Run Type` = str_to_title(str_trim(`Run Type`)),
      Result = str_to_title(str_trim(Result)),
      `Failure Attribution` = if_else(
        is.na(`Failure Attribution`) | str_trim(`Failure Attribution`) == "",
        NA_character_,
        str_to_title(str_trim(`Failure Attribution`))
      ),
      Run_Day = as_date(Date)
    ) %>%
    filter(!is.na(Date), Result %in% c("Pass", "Fail"))
}

runs_data <- read_runs() %>% clean_runs()
latest_run_at <- max(runs_data$Date, na.rm = TRUE)

# Release Deployment data (separate tab)
read_release_deployment_runs <- function() {
  auth_gs()
  googlesheets4::read_sheet(
    ss = AUTOMATION_SHEET_ID,
    sheet = RELEASE_DEPLOYMENT_SHEET_TAB,
    range = RUNS_SHEET_RANGE,
    col_types = "cccc"
  )
}

clean_release_runs <- function(df) {
  df %>%
    rename_with(~str_trim(.x)) %>%
    mutate(
      Date = parse_date_time(
        Date,
        orders = c("ymd HMS", "mdy HMS", "ymd HM", "mdy HM", "ymd", "mdy"),
        tz = RUNS_TZ
      ),
      Result = str_to_title(str_trim(Result)),
      Run_Day = as_date(Date)
    ) %>%
    filter(!is.na(Date), Result %in% c("Pass", "Fail"))
}

release_deployment_data <- tryCatch(
  read_release_deployment_runs() %>% clean_release_runs(),
  error = function(e) tibble(Date = as.POSIXct(character()), Result = character(), Run_Day = as.Date(character()))
)
```

Summary
=====================================

Row
-------------------------------------

### 7-Day Pass Rate

```{r exec_kpi_pass_rate_7d}
latest_day <- max(runs_data$Run_Day, na.rm = TRUE)
last_7_cutoff <- latest_day - days(6)

kpi_7d <- runs_data %>%
  filter(Run_Day >= last_7_cutoff) %>%
  summarise(
    Total = n(),
    Passed = sum(Result == "Pass"),
    Failed = sum(Result == "Fail"),
    Pass_Rate = if_else(Total == 0, NA_real_, Passed / Total)
  )

valueBox(
  value = ifelse(is.na(kpi_7d$Pass_Rate), "N/A", scales::percent(kpi_7d$Pass_Rate, accuracy = 0.1)),
  caption = vb_caption(
    "7-day pass rate",
    paste0("Last 7 days • ", kpi_7d$Passed, " / ", kpi_7d$Total, " runs passed")
  ),
  color = ifelse(is.na(kpi_7d$Pass_Rate), "primary", ifelse(kpi_7d$Pass_Rate >= 0.95, "success", ifelse(kpi_7d$Pass_Rate >= 0.85, "warning", "danger")))
)
```

### Failed Runs (7 Days)

```{r exec_kpi_fails_7d}
valueBox(
  value = scales::comma(kpi_7d$Failed),
  caption = vb_caption(
    "Failed runs (7d)",
    paste0("Last 7 days • ", scales::comma(kpi_7d$Total), " total runs")
  ),
  color = ifelse(kpi_7d$Failed == 0, "success", ifelse(kpi_7d$Failed <= 5, "warning", "danger"))
)
```

### Untriaged Failures (30 Days)

```{r exec_kpi_untriaged_30d}
last_30_cutoff <- latest_day - days(29)

failures_30d <- runs_data %>%
  filter(Run_Day >= last_30_cutoff, Result == "Fail") %>%
  mutate(
    `Failure Attribution` = if_else(
      is.na(`Failure Attribution`) | str_trim(`Failure Attribution`) == "",
      "Needs Triage",
      `Failure Attribution`
    )
  ) %>%
  summarise(
    Total_Failures = n(),
    Needs_Triage = sum(`Failure Attribution` == "Needs Triage"),
    Needs_Triage_Rate = if_else(Total_Failures == 0, 0, Needs_Triage / Total_Failures)
  )

valueBox(
  value = scales::percent(failures_30d$Needs_Triage_Rate, accuracy = 0.1),
  caption = vb_caption(
    "Untriaged share (30d)",
    paste0(failures_30d$Needs_Triage, " of ", failures_30d$Total_Failures, " failures still untriaged")
  ),
  color = ifelse(failures_30d$Needs_Triage_Rate <= 0.05, "success", ifelse(failures_30d$Needs_Triage_Rate <= 0.15, "warning", "danger"))
)
```

### Release Deployment Pass Rate (30 Days)

```{r exec_kpi_release_pass_rate_30d}
release_30d <- release_deployment_data %>%
  filter(Run_Day >= last_30_cutoff) %>%
  summarise(
    Total = n(),
    Passed = sum(Result == "Pass"),
    Pass_Rate = if_else(Total == 0, NA_real_, Passed / Total)
  )

valueBox(
  value = ifelse(is.na(release_30d$Pass_Rate), "N/A", scales::percent(release_30d$Pass_Rate, accuracy = 0.1)),
  caption = ifelse(
    release_30d$Total == 0,
    vb_caption("Release pass rate (30d)", "No release deployment runs in the last 30 days"),
    vb_caption(
      "Release pass rate (30d)",
      paste0("Last 30 days • ", release_30d$Passed, " / ", release_30d$Total, " release runs passed")
    )
  ),
  color = ifelse(is.na(release_30d$Pass_Rate), "primary", ifelse(release_30d$Pass_Rate >= 0.95, "success", ifelse(release_30d$Pass_Rate >= 0.85, "warning", "danger")))
)
```


Automation Runs
=====================================

Row
-------------------------------------

###
```{r monthly_avg_pass_rate}
monthly_df <- runs_data %>%
  group_by(
    Month = floor_date(Run_Day, "month")
  ) %>%
  summarise(
    Total = n(),
    Passed = sum(Result == "Pass"),
    Avg_Pass_Rate = Passed / Total,
    .groups = "drop"
  ) %>%
  arrange(Month) %>%
  mutate(
    Rolling_Avg_3M = roll_mean(Avg_Pass_Rate, n = 3, align = "right", fill = NA)
  )

# Calculate trend
monthly_df <- monthly_df %>%
  mutate(Month_num = as.numeric(Month - min(Month, na.rm = TRUE)))
valid_data <- monthly_df %>% filter(!is.na(Avg_Pass_Rate) & !is.na(Month_num))
if (nrow(valid_data) >= 2) {
  model <- lm(Avg_Pass_Rate ~ Month_num, data = valid_data)
  monthly_df <- monthly_df %>% mutate(Trend_Line = predict(model, newdata = monthly_df))
} else {
  monthly_df <- monthly_df %>% mutate(Trend_Line = NA_real_)
}
monthly_df <- monthly_df %>% select(-Month_num)

# Trend direction
trend_dir <- get_trend_direction(monthly_df, Avg_Pass_Rate)
trend_emoji <- switch(trend_dir, "improving" = "📈", "declining" = "📉", "stable" = "➡️")

p <- ggplot(monthly_df, aes(Month, Avg_Pass_Rate, group = 1)) +
  geom_line(aes(y = Trend_Line), color = "#E69F00", linewidth = 1.5, linetype = "dashed", alpha = 0.7, na.rm = TRUE) +
  geom_line(color = "#5bc0de", linewidth = 1) +
  geom_point(color = "#5bc0de", size = 2) +
  geom_line(aes(y = Rolling_Avg_3M), color = "#009E73", linewidth = 1.5, linetype = "solid", na.rm = TRUE) +
  pass_rate_goal_gg_hline(AUTOMATION_PASS_RATE_GOAL) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(x = NULL, y = "Average Pass Rate") +
  BASE_THEME

ggplotly(p, tooltip = c("text", "y")) %>%
  layout(
    title = list(text = paste0("<b>Average Passing Rate per Month ", trend_emoji, "</b>"), x = 0.02, xanchor = "left"),
    plot_bgcolor = "#1f1f1f",
    paper_bgcolor = "#1f1f1f",
    yaxis = list(tickformat = ".0%"),
    annotations = c(
      pass_rate_goal_annotation(AUTOMATION_PASS_RATE_GOAL),
      list(x = 0.98, y = 0.05, xref = "paper", yref = "paper", text = "— · · — 3-mo avg", showarrow = FALSE, font = list(color = "#009E73", size = 10))
    )
  ) %>%
  add_plotly_border()
```

Row
-------------------------------------

###
```{r weekly_avg_pass_rate}
weekly_df <- runs_data %>%
  group_by(
    Week = floor_date(Run_Day, "week", week_start = 1)
  ) %>%
  summarise(
    Total = n(),
    Passed = sum(Result == "Pass"),
    Avg_Pass_Rate = Passed / Total,
    .groups = "drop"
  ) %>%
  arrange(Week)

p <- ggplot(
  weekly_df,
  aes(
    Week,
    Avg_Pass_Rate,
    group = 1,
    text = paste0(
      "Week of: ", format(Week, "%b %d, %Y"),
      "<br>Avg Pass Rate: ", scales::percent(Avg_Pass_Rate, accuracy = 0.1)
    )
  )
) +
  geom_line(color = "#5bc0de", linewidth = 1) +
  geom_point(color = "#5bc0de", size = 2) +
  pass_rate_goal_gg_hline(AUTOMATION_PASS_RATE_GOAL) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(x = NULL, y = "Average Pass Rate") +
  BASE_THEME

ggplotly(p, tooltip = "text") %>%
  layout(
    title = plotly_title("Average Passing Rate per Week"),
    plot_bgcolor = "#1f1f1f",
    paper_bgcolor = "#1f1f1f",
    yaxis = list(tickformat = ".0%"),
    annotations = pass_rate_goal_annotation(AUTOMATION_PASS_RATE_GOAL)
  ) %>%
  add_plotly_border()
```

Row
-------------------------------------

###

```{r daily_pass_rate}
df <- runs_data %>%
  group_by(Run_Day) %>%
  summarise(
    Total = n(),
    Passed = sum(Result == "Pass"),
    Failed = sum(Result == "Fail"),
    Pass_Rate = Passed / Total,
    .groups = "drop"
  ) %>%
  arrange(Run_Day) %>%
  mutate(
    Rolling_Avg_7D = roll_mean(Pass_Rate, n = 7, align = "right", fill = NA),
    Rolling_Avg_30D = roll_mean(Pass_Rate, n = 30, align = "right", fill = NA)
  )

# Calculate linear trend
df <- df %>% mutate(Run_Day_num = as.numeric(Run_Day - min(Run_Day, na.rm = TRUE)))
valid_df <- df %>% filter(!is.na(Pass_Rate) & !is.na(Run_Day_num))
if (nrow(valid_df) >= 2) {
  model <- lm(Pass_Rate ~ Run_Day_num, data = valid_df)
  df <- df %>% mutate(Trend_Line = predict(model, newdata = df))
} else {
  df <- df %>% mutate(Trend_Line = NA_real_)
}
df <- df %>% select(-Run_Day_num)

# Trend direction
trend_dir <- get_trend_direction(df, Pass_Rate)
trend_emoji <- switch(trend_dir, "improving" = "📈", "declining" = "📉", "stable" = "➡️")

# Detect anomalies
df <- df %>% detect_anomalies_zscore("Pass_Rate", threshold = 2)

# Count anomalies for display
anomaly_count <- sum(df$is_anomaly, na.rm = TRUE)
anomaly_alert <- ifelse(anomaly_count > 0, paste0(" ⚠️ ", anomaly_count, " anomaly(s)"), "")

p <- ggplot(df, aes(Run_Day, Pass_Rate, group = 1)) +
  geom_line(aes(y = Trend_Line), color = "#E69F00", linewidth = 1.5, linetype = "dashed", alpha = 0.7, na.rm = TRUE) +
  geom_line(aes(y = Rolling_Avg_30D), color = "#D55E00", linewidth = 2, linetype = "dotdash", alpha = 0.8, na.rm = TRUE) +
  geom_line(aes(y = Rolling_Avg_7D), color = "#009E73", linewidth = 1.5, na.rm = TRUE) +
  geom_line(color = "#5bc0de", linewidth = 1) +
  geom_point(
    data = df %>% filter(is_anomaly == TRUE),
    aes(Run_Day, Pass_Rate),
    color = "#D55E00", size = 8, shape = 21, fill = "#D55E00", stroke = 2
  ) +
  geom_point(color = "#5bc0de", size = 2) +
  pass_rate_goal_gg_hline(AUTOMATION_PASS_RATE_GOAL) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(
    x = NULL,
    y = "Pass Rate",
    subtitle = paste(
      "Latest run:",
      format(latest_run_at, "%b %d, %H:%M", tz = RUNS_TZ),
      RUNS_TZ
    )
  ) +
  BASE_THEME

ggplotly(p, tooltip = c("text", "y")) %>%
  layout(
    title = list(text = paste0("<b>Daily Pass Rate ", trend_emoji, "</b>"), x = 0.02, xanchor = "left"),
    plot_bgcolor = "#1f1f1f",
    paper_bgcolor = "#1f1f1f",
    yaxis = list(tickformat = ".0%"),
    annotations = c(
      pass_rate_goal_annotation(AUTOMATION_PASS_RATE_GOAL),
      list(x = 0.98, y = 0.05, xref = "paper", yref = "paper", text = "— 7-day · · — 30-day", showarrow = FALSE, font = list(color = "#777777", size = 9))
    )
  ) %>%
  add_plotly_border()
```
  ) +
  BASE_THEME

ggplotly(p, tooltip = "text") %>%
  layout(
    title = plotly_title("Daily Pass Rate"),
    plot_bgcolor = "#1f1f1f",
    paper_bgcolor = "#1f1f1f",
    yaxis = list(tickformat = ".0%"),
    annotations = pass_rate_goal_annotation(AUTOMATION_PASS_RATE_GOAL)
  ) %>%
  add_plotly_border()
```

Failure Attribution
=====================================

Row
-------------------------------------

### 

```{r daily_failures_by_attribution}
attribution_levels <- c(
  "Test Bug",
  "Product Change",
  "Product Bug",
  "Platform Issue",
  "Needs Triage"
)

attribution_colors <- c(
  "Test Bug" = "#5bc0de",
  "Product Change" = "#f0ad4e",
  "Product Bug" = "#d9534f",
  "Platform Issue" = "#9e56bf",
  "Needs Triage" = "#7F7F7F"
)

df <- runs_data %>%
  filter(Result == "Fail") %>%
  mutate(
    `Failure Attribution` = if_else(
      is.na(`Failure Attribution`),
      "Needs Triage",
      `Failure Attribution`
    )
  ) %>%
  count(Run_Day, `Failure Attribution`, name = "Failures") %>%
  complete(
    Run_Day,
    `Failure Attribution` = attribution_levels,
    fill = list(Failures = 0)
  )

p <- ggplot(
  df,
  aes(Run_Day, Failures, fill = `Failure Attribution`)
) +
  geom_col(width = 0.85) +
  scale_fill_manual(values = attribution_colors) +
  labs(x = NULL, y = "Failures") +
  BASE_THEME +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(p) %>%
  layout(
    title = plotly_title("Daily Failures by Attribution"),
    barmode = "stack",
    plot_bgcolor = "#1f1f1f",
    paper_bgcolor = "#1f1f1f",
    legend = list(orientation = "h", x = 0.02, y = -0.25)
  ) %>%
  add_plotly_border()
```

Operations Load
=====================================

Row
-------------------------------------

### 

```{r daily_run_volume}
df <- runs_data %>%
  count(Run_Day, Result, name = "Runs") %>%
  tidyr::complete(Run_Day, Result = c("Pass", "Fail"), fill = list(Runs = 0))

p <- ggplot(
  df,
  aes(
    Run_Day,
    Runs,
    fill = Result,
    text = paste0(
      "Run Day: ", Run_Day,
      "<br>Result: ", Result,
      "<br>Runs: ", Runs
    )
  )
) +
  geom_col(width = 0.85) +
  scale_fill_manual(values = c("Pass" = "#009E73", "Fail" = "#D55E00")) +
  labs(x = NULL, y = "Run Count") +
  BASE_THEME +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplotly(p, tooltip = "text") %>%
  layout(
    title = plotly_title("Daily Automation Volume (Pass vs Fail)"),
    barmode = "stack",
    plot_bgcolor = "#1f1f1f",
    paper_bgcolor = "#1f1f1f",
    legend = list(orientation = "h", x = 0.02, y = -0.2)
  ) %>%
  add_plotly_border()
```

Release Deployment
=====================================

Row
-------------------------------------

###
```{r release_deployment_monthly_pass_rate}
monthly_release_df <- release_deployment_data %>%
  group_by(
    Month = floor_date(Run_Day, "month")
  ) %>%
  summarise(
    Total = n(),
    Passed = sum(Result == "Pass"),
    Avg_Pass_Rate = Passed / Total,
    .groups = "drop"
  ) %>%
  arrange(Month)

p <- ggplot(
  monthly_release_df,
  aes(
    Month,
    Avg_Pass_Rate,
    group = 1,
    text = paste0(
      "Month: ", format(Month, "%b %Y"),
      "<br>Avg Pass Rate: ", scales::percent(Avg_Pass_Rate, accuracy = 0.1)
    )
  )
) +
  geom_line(color = "#5bc0de", linewidth = 1) +
  geom_point(color = "#5bc0de", size = 2) +
  pass_rate_goal_gg_hline(RELEASE_PASS_RATE_GOAL) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(x = NULL, y = "Average Pass Rate") +
  BASE_THEME

ggplotly(p, tooltip = "text") %>%
  layout(
    title = plotly_title("Release Deployment: Average Pass Rate per Month"),
    plot_bgcolor = "#1f1f1f",
    paper_bgcolor = "#1f1f1f",
    yaxis = list(tickformat = ".0%"),
    annotations = pass_rate_goal_annotation(RELEASE_PASS_RATE_GOAL)
  ) %>%
  add_plotly_border()
```



Flaky Test Detection
=====================================

Row {data-height=200}
-------------------------------------

### Flaky Tests Detected (Last 30 Days)

```{r flaky_test_kpi}
# Detect flaky tests: tests that flip between pass/fail frequently
flaky_threshold <- 0.2  # 20% flip rate threshold

flaky_analysis <- runs_data %>%
  filter(Run_Day >= Sys.Date() - days(30)) %>%
  group_by(`Run Type`) %>%
  summarise(
    Total_Runs = n(),
    Pass_Count = sum(Result == "Pass"),
    Fail_Count = sum(Result == "Fail"),
    Pass_Rate = Pass_Count / Total_Runs,
    Is_Flaky = Pass_Rate > flaky_threshold & Pass_Rate < (1 - flaky_threshold),
    .groups = "drop"
  )

flaky_count <- sum(flaky_analysis$Is_Flaky, na.rm = TRUE)
flaky_tests <- flaky_analysis %>% filter(Is_Flaky == TRUE) %>% pull(`Run Type`)

valueBox(
  value = flaky_count,
  caption = vb_caption(
    "Flaky Tests (30d)",
    ifelse(flaky_count > 0, paste0("Tests with 20-80% pass rate: ", paste(flaky_tests, collapse = ", ")), "No flaky tests detected")
  ),
  color = ifelse(flaky_count == 0, "success", ifelse(flaky_count <= 2, "warning", "danger"))
)
```

### Test Stability Score

```{r stability_score_kpi}
# Calculate overall stability: percentage of tests that are NOT flaky
if (nrow(flaky_analysis) > 0) {
  stability_score <- (sum(!flaky_analysis$Is_Flaky, na.rm = TRUE) / nrow(flaky_analysis))
} else {
  stability_score <- 1
}

valueBox(
  value = scales::percent(stability_score, accuracy = 1),
  caption = vb_caption(
    "Test Stability Score",
    paste0("Percentage of stable tests (flip rate < 20%)")
  ),
  color = ifelse(stability_score >= 0.90, "success", ifelse(stability_score >= 0.75, "warning", "danger"))
)
```

### Needs Investigation

```{r needs_investigation_kpi}
investigate_count <- flaky_analysis %>%
  filter(Pass_Rate >= 0.05 & Pass_Rate <= 0.95 & Total_Runs >= 5) %>%
  nrow()

valueBox(
  value = investigate_count,
  caption = vb_caption(
    "Tests Needing Review",
    "Tests with 5-95% pass rate and 5+ runs"
  ),
  color = ifelse(investigate_count == 0, "success", "warning")
)
```

Row {data-height=500}
-------------------------------------

### Test Pass Rate Distribution

```{r flaky_distribution}
# Show distribution of pass rates across all tests
df <- runs_data %>%
  filter(Run_Day >= Sys.Date() - days(30)) %>%
  group_by(`Run Type`) %>%
  summarise(
    Total = n(),
    Passed = sum(Result == "Pass"),
    Pass_Rate = ifelse(Total > 0, Passed / Total, NA),
    .groups = "drop"
  ) %>%
  filter(!is.na(Pass_Rate), Total >= 3)

if (nrow(df) == 0) {
  plotly_empty(type = "bar") %>%
    layout(title = plotly_title("Test Pass Rate Distribution (Last 30 Days)"))
} else {
  # Categorize tests
  df <- df %>%
    mutate(
      Category = case_when(
        Pass_Rate >= 0.95 ~ "Stable (Pass)",
        Pass_Rate <= 0.05 ~ "Stable (Fail)",
        Pass_Rate >= 0.20 & Pass_Rate <= 0.80 ~ "Flaky",
        TRUE ~ "Marginally Stable"
      ),
      Category = factor(Category, levels = c("Stable (Pass)", "Marginally Stable", "Flaky", "Stable (Fail)"))
    )
  
  # Color by category
  cat_colors <- c(
    "Stable (Pass)" = "#009E73",
    "Marginally Stable" = "#E69F00", 
    "Flaky" = "#D55E00",
    "Stable (Fail)" = "#7F7F7F"
  )
  
  plot_ly(
    data = df,
    x = ~reorder(`Run Type`, Pass_Rate),
    y = ~Pass_Rate,
    color = ~Category,
    colors = cat_colors,
    type = "bar",
    marker = list(line = list(color = "#1f1f1f", width = 1)),
    hovertemplate = paste0(
      "Test: %{x}<br>",
      "Pass Rate: %{y:.1%}<br>",
      "Runs: %{customdata}<extra></extra>"
    ),
    customdata = ~Total
  ) %>%
    layout(
      title = plotly_title("Test Pass Rate Distribution (Last 30 Days)"),
      plot_bgcolor = "#1f1f1f",
      paper_bgcolor = "#1f1f1f",
      xaxis = list(
        title = "",
        showgrid = FALSE,
        tickangle = 45
      ),
      yaxis = list(
        title = "Pass Rate",
        tickformat = ".0%",
        showgrid = TRUE,
        gridcolor = "#333333",
        range = c(0, 1)
      ),
      legend = list(
        orientation = "h",
        x = 0.5,
        y = -0.2,
        xanchor = "center",
        font = list(color = "#ffffff")
      )
    ) %>%
    add_plotly_border()
}
```

Row {data-height=500}
-------------------------------------

### Tests Requiring Attention

```{r flaky_tests_table}
# Table of flaky/marginal tests
df <- runs_data %>%
  filter(Run_Day >= Sys.Date() - days(30)) %>%
  group_by(`Run Type`) %>%
  summarise(
    Total_Runs = n(),
    Passed = sum(Result == "Pass"),
    Failed = sum(Result == "Fail"),
    Pass_Rate = Passed / Total_Runs,
    Flip_Rate = 2 * min(Passed, Failed) / Total_Runs,
    .groups = "drop"
  ) %>%
  filter(Total_Runs >= 5, Pass_Rate > 0.05, Pass_Rate < 0.95) %>%
  arrange(Pass_Rate) %>%
  mutate(
    Priority = case_when(
      Pass_Rate < 0.20 | Pass_Rate > 0.80 ~ "Low",
      Pass_Rate < 0.35 | Pass_Rate > 0.65 ~ "Medium",
      TRUE ~ "High"
    )
  )

if (nrow(df) == 0) {
  cat("No tests requiring attention (need 5+ runs with 5-95% pass rate)")
} else {
  reactable(
    df,
    theme = REACTABLE_THEME_DARK,
    searchable = TRUE,
    pagination = TRUE,
    defaultPageSize = 10,
    highlight = TRUE,
    bordered = TRUE,
    compact = TRUE,
    defaultSorted = "Flip_Rate",
    defaultSortOrder = "desc",
    defaultColDef = colDef(vAlign = "top"),
    columns = list(
      `Run Type` = colDef(width = 250, minWidth = 200),
      Total_Runs = colDef(width = 100, name = "Runs"),
      Passed = colDef(width = 80),
      Failed = colDef(width = 80),
      Pass_Rate = colDef(
        width = 100,
        name = "Pass Rate",
        cell = function(value) scales::percent(value, accuracy = 0.1)
      ),
      Flip_Rate = colDef(
        width = 100,
        name = "Flip Rate",
        cell = function(value) scales::percent(value, accuracy = 0.1)
      ),
      Priority = colDef(
        width = 100,
        cell = function(value) {
          color <- switch(value, "High" = "#D55E00", "Medium" = "#E69F00", "#009E73")
          htmltools::div(
            style = list(
              display = "inline-block",
              padding = "3px 10px",
              borderRadius = "999px",
              background = color,
              color = "#111111",
              fontWeight = 700,
              fontSize = "12px"
            ),
            value
          )
        }
      )
    )
  )
}
```
